---
title: "mseptools"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mseptools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mseptools)
```

## Example  

### Examine Data  

We'll work with the built-in 2019 salinity dataset.

``` {r}
dat <- mssnd_salinity2019
```

Look at the head of the main data frame. This contains salinity readings at 30-minute intervals.  

```{r}
head(dat$data)
```

Look at the head of the daily averages data frame.  

```{r}
head(dat$daily)
```

Something strange might be going on with January 1st.  

```{r}
dat$daily |> 
    dplyr::arrange(date) |> 
    head()
```

Yes, I probably need to fix something inside the function that calculates daily averages - there's probably some UTC-to-LST conversion issue.  


And let's see what's in the site info data frame.  

```{r}
head(dat$siteInfo)
```


For mapping and graphing of this dataset, check out the 'Maps and Plots' article.  
