---
title: "Maps and Plots"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mseptools)
```

### Examine Data  

We'll work with the built-in 2019 salinity dataset.

``` {r}
dat <- mssnd_salinity2019
```

Look at the head of the main data frame. This contains salinity readings at 30-minute intervals.  

```{r}
head(dat$data)
```

Look at the head of the daily averages data frame.  

```{r}
head(dat$daily)
```

Something strange might be going on with January 1st.  

```{r}
dat$daily |> 
    dplyr::arrange(date) |> 
    head()
```

Yes, I probably need to fix something inside the function that calculates daily averages - there's probably some UTC-to-LST conversion issue.  


And let's see what's in the site info data frame.  

```{r}
head(dat$siteInfo)
```

### Plot  

This graph uses `plotly`, which makes the graphics interactive. In addition to hovering over parts of the graph to see the exact values, you can click on a legend entry to remove (or re-show) a station; double-click to show *only* that station. There is a slider bar below so you can narrow the date range. 

``` {r}
plot_mssnd_salinity(dat)
```  

### Map the stations  

This function uses `leaflet` to show the USGS monitoring stations on a map.  

``` {r}
map_mssnd_usgs(dat$siteInfo)
```

### Color palette  

`plot_mssnd_salinity()` takes a named vector of colors; `leaflet` does not. A common palette can be created and used in both functions as follows:  

``` {r}
stns <- sort(dat$siteInfo$clean_nm)

# static color palette
colors_static <- as.character(khroma::color("roma")(length(stns)))
names(colors_static) <- stns

# color function
color_function <- leaflet::colorFactor(palette = colors_static,
                                       domain = names(colors_static))

# plot and map with these palettes
plot_mssnd_salinity(dat, colors = colors_static)
map_mssnd_usgs(dat$siteInfo, color_function = color_function)
```
